Supplementary material to: Drug sensitivity prediction with the normal inverse Gaussian prior informed by external data

### 2019-11-22 docs/supplement1.Rnw
fixed error in simulation_gdsc.R simulation 3

  equations in MD equations (\ref{md-eq:vbequations}).

@@

  \section{Gibbs sampler}\label{sec:gibbssampler}
  MCMC samples from the posterior corresponding to model 
  (\ref{md-eq:prior}) may be generated for each equation independently. 
  MCMC samples may be generated by iteratively sampling the following 
  conditional distributions:
  \begin{subequations}
    \begin{align}
      \bm{\beta}_d | \bgamma_d^2, \sigma_d^2, \tau_d^2, \y_d & \sim 
      \mathcal{N}_p (\bm{\mu}_d, \bm{\Sigma}_d), \label{eq:betasample} \\
      \text{with } & \bm{\Sigma}_d = \sigma_d^2 [\X \tr \X + 
      \tau_d^{-2} \diag (\gamma_{jd}^{-2})]^{-1}, \label{eq:sigmasample} \\
      \text{and } & \bm{\mu}_d = [\X \tr \X + 
      \tau_d^{-2} \diag (\gamma_{jd}^{-2})]^{-1} \X \tr 
      \y_d \label{eq:musample}, \\
      \gamma_{jd}^2 | \beta_{jd}, \sigma_d^2, \tau_d^2, \y &
      \sim \mathcal{GIG}
      \(-1, \lambda_{\text{feat}}/ \phi_{jd}^{2}, \delta_{jd}\), \nonumber \\
      \text{with } & \delta_{jd} = \sigma_d^{-2} \tau_d^{-2} \beta_{jd}^2 + 
      \lambda_{\text{feat}}, \nonumber \\
      \tau_d^2 | \bm{\beta}_d, \sigma_d^2, \bgamma_{d}^2, \y & \sim
      \mathcal{GIG}
      \(-\frac{p+1}{2}, \lambda_{\text{drug}}/ \chi_{d}^{2}, \eta_d\), 
      \nonumber \\
      \text{with } & \eta_d = \sigma_d^{-2} \sum_{j=1}^p \gamma_{jd}^{-2}
      \beta_{jd}^2 + \lambda_{\text{drug}}, \nonumber \\
      \sigma_d^2 | \bm{\beta}_d, \bgamma_d^2, \tau_d^2, \y & \sim \Gamma^{-1} 
      \(\frac{n + p + 1}{2}, \zeta_d\), \nonumber \\
      \text{with } & \zeta_d = \frac{1}{2} \bigg[\mathbf{y} \tr \mathbf{y} -
      2 \mathbf{y} \tr \X \bm{\mu} + \trace ( \X \tr \X \bm{\Sigma}) + 
      (\bm{\mu}) \tr \X \tr \X \bm{\mu} + 
      \tau^{-2}_d \trace (\diag(\gamma_{jd}^{-2}) \bm{\Sigma}) \nonumber \\
      & \,\,\,\,\,\,\,\,\,\, + \tau_d^{-2} (\bm{\mu}) \tr 
      \diag(\gamma_{jd}^{-2}) \bm{\mu}\bigg]. \nonumber
    \end{align}
  \end{subequations}
  In high dimensional space, the $p \times p$ matrix inversions in 
  (\ref{eq:sigmasample}) and (\ref{eq:musample}) are   
  significant computational bottlenecks. \cite{bhattacharya_fast_2016} describe 
  a method to sample from (\ref{eq:betasample}) without explicit calculation
  of this inverse, thereby offering a siginifcant speed-up compared to naive
  sampling.

>>>>

  % equations in MD equations (\ref{md-eq:vbequations}).

@@

  \section{Gibbs sampler}\label{sec:gibbssampler}
  MCMC samples from the posterior corresponding to model 
  % (\ref{md-eq:prior}) may be generated for each equation independently. 
  MCMC samples may be generated by iteratively sampling the following 
  conditional distributions:
  \begin{subequations}
    \begin{align}
      \bm{\beta}_d | \bgamma_d^2, \sigma_d^2, \tau_d^2, \y_d & \sim 
      \mathcal{N}_p (\bm{\mu}_d, \bm{\Sigma}_d), \label{eq:betasample} \\
      \text{with } & \bm{\Sigma}_d = \sigma_d^2 [\X \tr \X + 
      \tau_d^{-2} \diag (\gamma_{jd}^{-2})]^{-1}, \label{eq:sigmasample} \\
      \text{and } & \bm{\mu}_d = [\X \tr \X + 
      \tau_d^{-2} \diag (\gamma_{jd}^{-2})]^{-1} \X \tr 
      \y_d \label{eq:musample}, \\
      \gamma_{jd}^2 | \beta_{jd}, \sigma_d^2, \tau_d^2, \y &
      \sim \mathcal{GIG}
      \(-1, \lambda_{\text{feat}}/ \phi_{jd}^{2}, \delta_{jd}\), \nonumber \\
      \text{with } & \delta_{jd} = \sigma_d^{-2} \tau_d^{-2} \beta_{jd}^2 + 
      \lambda_{\text{feat}}, \nonumber \\
      \tau_d^2 | \bm{\beta}_d, \sigma_d^2, \bgamma_{d}^2, \y & \sim
      \mathcal{GIG}
      \(-\frac{p+1}{2}, \lambda_{\text{drug}}/ \chi_{d}^{2}, \eta_d\), 
      \nonumber \\
      \text{with } & \eta_d = \sigma_d^{-2} \sum_{j=1}^p \gamma_{jd}^{-2}
      \beta_{jd}^2 + \lambda_{\text{drug}}, \nonumber \\
      \sigma_d^2 | \bm{\beta}_d, \bgamma_d^2, \tau_d^2, \y & \sim \Gamma^{-1} 
      \(\frac{n + p + 1}{2}, \zeta_d\), \nonumber \\
      \text{with } & \zeta_d = \frac{1}{2} \bigg[\mathbf{y} \tr \mathbf{y} -
      2 \mathbf{y} \tr \X \bm{\mu} + \trace ( \X \tr \X \bm{\Sigma}) + 
      (\bm{\mu}) \tr \X \tr \X \bm{\mu} + 
      \tau^{-2}_d \trace (\diag(\gamma_{jd}^{-2}) \bm{\Sigma}) \nonumber \\
      & \,\,\,\,\,\,\,\,\,\, + \tau_d^{-2} (\bm{\mu}) \tr 
      \diag(\gamma_{jd}^{-2}) \bm{\mu}\bigg]. \nonumber
    \end{align}
  \end{subequations}
  In high dimensional space, the $p \times p$ matrix inversions in 
  (\ref{eq:sigmasample}) and (\ref{eq:musample}) are   
  significant computational bottlenecks. \cite{bhattacharya_fast_2016} describe 
  a method to sample from (\ref{eq:betasample}) without explicit calculation
  of this inverse, thereby offering a siginifcant speed-up compared to naive
  sampling.
